Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-04-23 paper.Rmd
name correction Alice
added reference to DigComp

As mentioned above, the following competence area's were identified as relevant for the tutorials: 1. Information and data literacy, 2. Communication and collaboration, 3. Digital content creation and, 5. Problem solving [@europeancommissionjointresearchcentre2022]. In these competence area's various competences are developed towards an advanced or even specialised level.

@@

-   February 2022-July 2023: Alice Overgaauw, Johan Broersma, Mandy Hazenberg, Paulina Fulneczek, Ties Heesink and their tutor: Jan Willem Huson.

>>>>

As mentioned above, the following competence area's were identified as relevant for the tutorials: 1. Information and data literacy, 2. Communication and collaboration, 3. Digital content creation and, 5. Problem solving [@europeancommissionjointresearchcentre2022]. In these competence area's various competences are developed towards an advanced or even specialised level. A more extensive description of the Digital Competence Framework for Citizens in relation to Agent-Based Modelling for archaeologists is also available [@visser2024].

@@

-   February 2022-July 2023: Alice Poorthuis, Johan Broersma, Mandy Hazenberg, Paulina Fulneczek, Ties Heesink and their tutor: Jan Wille

### 2024-04-23 paper.tex
name correction Alice
added reference to DigComp

\title{Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists}
\author{true \and true \and true \and true \and true \and true \and true \and true \and true}
\date{April 10, 2024}

@@

As mentioned above, the following competence area's were identified as relevant for the tutorials: 1. Information and data literacy, 2. Communication and collaboration, 3. Digital content creation and, 5. Problem solving (European Commission, Joint Research Centre et al. 2022). In these competence area's various competences are developed towards an advanced or even specialised level.

@@

\begin{itemize}
\item
  September 2022-February 2023: Dany Dragoi, Liam van den Bosch, Marko Stojkovic, Max van Duinen, Nora van den Engel, Roan Man, Stefan Oostingh and their tutor: Mark Spanjer.
\item
  February 2022-July 2023: Alice Overgaauw, Johan Broersma, Mandy Hazenberg, Paulina Fulneczek, Ties Heesink and their tutor: Jan Willem Huson.
\item
  September 2023-February 2024: Arnfinn Sijbrant, Eva Baan, Jip Mulder, Robert Aalpoel, Sem Lucas, Sterre Regts and their tutor: Jan Willem Huson.
\end{itemize}

@@

>>>>

\title{Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists}
\author{true \and true \and true \and true \and true \and true \and true \and true \and true}
\date{April 23, 2024}

@@

As mentioned above, the following competence area's were identified as relevant for the tutorials: 1. Information and data literacy, 2. Communication and collaboration, 3. Digital content creation and, 5. Problem solving (European Commission, Joint Research Centre et al. 2022). In these competence area's various competences are developed towards an advanced or even specialised level. A more extensive description of the Digital Competence Framework for Citizens in relation to Agent-Based Modelling for archaeologists is also available (Visser et al. 2024).

@@

\begin{itemize}
\item
  September 2022-February 2023: Dany Dragoi, Liam van den Bosch, Marko Stojkovic, Max van Duinen, Nora van den Engel, Roan Man, Stefan Oostingh and their tutor: Mark Spanjer.
\item
  February 2022-July 2023: Alice Poorthuis, Johan Broersma, Mandy Hazenberg, Paulina Fulneczek, Ties Heesink and their tutor: Jan Wille
\item
  September 2023-February 2024: Arnfinn Sijbrant, Eva Baan, Jip Mulder, Robert Aalpoel, Sem Lucas, Sterre Regts and their tutor: Jan Willem Huson.
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-visser2024}{}}%
Visser, R, Lambers, K, Aitchison, K, Jutte, A, Rocks-Macqueen, D, Knaap, L van der, Romanowska, I and Brughmans, T. 2024 \emph{The Digital Competence Framework for Citizens (2.2) and Agent-Based modelling for Archaeologists}. DOI: https://doi.org/\href{https://doi.org/10.5281/zenodo.11046488}{10.5281/zenodo.11046488}.
